Efficiently Handling Guards in the Low Level Design of RPython's tracing JIT

### 2012-07-30 talk/vmil2012/paper.tex
add calculated resume data size to asm and guard size table

\begin{figure*}
    \include{figures/ops_count_table}
    \caption{Relative numbers of operations in the traces generated for
    different benchmarks}
    \label{fig:ops_count}
\end{figure*}
Although there are several publications about tracing just-in-time compilers, to
our knowledge, there are none that describe the use and implementation of
guards in this context. With the following contributions we aim to shed some
light (to much?) on this topic.
The contributions of this paper are:
\todo{more motivation}
Based on the informal observation that guards are among the most common
operations in the traces produced by PyPy's tracing JIT and that guards are
operations that are associated with an overhead to maintain information about
state to be able to rebuild it, our goal is to present concrete numbers for the
frecuency and the overhead produced by guards, explain how they are implemented
in the diferent levels of PyPy's tracing JIT and explain the rationale behind
the desing decisions based on the numbers.
\todo{extend}
\todo{contributions, description of PyPy's guard architecture, analysis on benchmarks}
\begin{itemize}
 \item
\end{itemize}

>>>>

\begin{figure*}
    \include{figures/ops_count_table}
    \caption{Relative numbers of operations in the traces generated for
    different benchmarks}
    \label{fig:ops_count}
\end{figure*}
Although there are several publications about tracing just-in-time compilers, to
our knowledge, there are none that describe the use and implementation of
guards in this context. With the following contributions we aim to shed some
light (to much?) on this topic.
The contributions of this paper are:
\todo{more motivation}
Based on the informal observation that guards are among the most common
operations in the traces produced by PyPy's tracing JIT and that guards are
operations that are associated with an overhead to maintain information about
state to be able to rebuild it, our goal is to present concrete numbers for the
frequency and the overhead produced by guards, explain how they are implemented
in the different levels of PyPy's tracing JIT and explain the rationale behind
the design decisions based on the numbers.
As can be seen on Figure~\ref{fig:ops_count} guards account for 14.42\% to
22.32\% of the operations before and for 15.2\% to 20.12\% of after the
optimization pass over the traced and compiled paths of the benchmarks.
Figure~\ref{fig:benchmarks} shows the absolute number of operations for each
benchmark, for every guard that stays alive after optimization there are
several kinds of metadata created and stored at different levels of the JIT to
be able to rebuild the interpreter or tracer state from a guard failure making
the optimization \bivab{some good word} of guards an important aspect of the
low-level design of a tracing just-in-time compiler.
\todo{extend}
\todo{contributions, description of PyPy's guard architecture, analysis on benchmarks}
\begin{itemize}
 \item
\end{itemize}
